---
title: "Ghost Crab Analysis"
output:
  html_document: default
  pdf_document: default
---
## Concept
Exploration of the Ghost Crab's burrow dimensions and burrow morphology

### Goals of Crab Analysis Project 
1. Load data from [Ghost Crab Burrow Morphology and Distribution](https://doi.org/10.6084/m9.figshare.6895109) 
2. Select and filter through burrow dimensions data 
2. Plot and graph selected data

### Required Packages
```{r, eval=FALSE}
library(tidyverse)
library(magrittr)
library(knitr)
```

```{r load-packages, include=FALSE}
library(magrittr)
library(knitr)
library(tidyverse)
```

### Part I
**Import data from [Ghost Crab Burrow Morphology and Distribution](https://doi.org/10.6084/m9.figshare.6895109).**
```{r,echo=FALSE, cache=TRUE}
burrow_dimensions_raw <- read.csv("../Data/Ghost_crab_burrow_architecture.csv")
head(burrow_dimensions_raw, n = 2)
```

Selecting and filtering for specific sites, depth, temperature, and month.
```{r,echo=FALSE}
burrow_site_depth_temp_month <- burrow_dimensions_raw %>%
  select(site, burrow.depth, burrow.temperature, month) %>%
  filter(site == "Debidue Island" | site == "Folly Beach " | site == "Pawleys Island 1" | site == "Edisto Beach")
head(burrow_site_depth_temp_month)
```

Selecting and filtering for specific burrow shape, sites, and temperature.
```{r, echo=FALSE}
burrow_shape_temperature_sites <- burrow_dimensions_raw %>%
  select(site, burrow.shape, burrow.temperature) %>%
  filter(site == "Debidue Island" | site == "Folly Beach " | site == "Pawleys Island 1" | site == "Edisto Beach")
head(burrow_shape_temperature_sites)
```

### Part II
**Looking for correlation between selected data**
```{r, echo=FALSE}
burrow_data_plot <- ggplot(burrow_site_depth_temp_month, aes(x = burrow.depth, y = burrow.temperature,
  color = month)) +
  geom_point() +
  facet_wrap(~site) +
  geom_smooth(method = "loess") +
  labs(x = "Burrow Depth (mm)", y = "Burrow Temperature (°C)") +
  labs(title = "Burrow Depth vs Temperature") +
  theme(plot.title = element_text(hjust = 0.5))
print(burrow_data_plot)
```

```{r, echo=FALSE}
burrow_data_plot_2 <- ggplot(burrow_shape_temperature_sites, aes(x = burrow.shape, y = burrow.temperature, color = burrow.shape)) +
  geom_point() +
  geom_jitter() +
  facet_wrap(~site)+
  labs(x = "Burrow Shape", y = "Burrow Temperature (°C)") +
  labs(title = "Burrow Shape vs Temperature") +
  theme(plot.title = element_text(hjust = 0.5))
print(burrow_data_plot_2)
```

## Conclusion
Further analysis is needed to conclude any findings.
